Random Forests

### 2020-07-05 pkg/circtree/inst/wind_paper/draft/JRSSC/rebuttal.tex

\setkomavar{subject}{Revision of `JRSS-SC-Jan-20-0007'}
\setkomavar{signature}{Moritz Lang\\Corresponding Author}

\setkomavar{fromname}[Name]{Moritz Lang}
\setkomavar{fromemail}{Moritz.Lang@uibk.ac.at}

\setkomavar{fromaddress}{University of Innsbruck, Department of Statistics, Universit\"atsstrasse
15, 6020 Innsbruck, Austria}

\begin{letter}[fromemail]{To Prof. Peter Smith}
\opening{Dear Prof.\ Smith,}

we thank you, as well as the associate editor and both reviewers, for the
positive and constructive feedback regarding our manuscript ``\textbf{Circular
Regression Trees and Forests with an Application to Probabilistic Wind
Direction Forecasting}''.

@@

\vspace{5mm}

Due to the COVID-19 pandemic our response took us longer than planned but
we have finally carefully revised our manuscript, incorporating the feedback
and suggestions. The most substantial changes in the manuscript are the following:

\begin{itemize}
\item We have fully revised the `Abstract' giving more emphasis to the application.
In addition, we now use the term `application' instead of `case study' throughout
the manuscript and have also renamed Sect.~4 accordingly.

\item In the section `Computational details', we have added information about the
order of magnitude of the computing time for the different methods on a standard desktop computer.

\item We now discuss the work of Hara and Chellappa~(2017) and their distribution-based 
tree algorithm in relation to our circular distributional trees within Sect.~1.1.

@@

\closing{Yours sincerely,}

\end{letter}

\newpage

\section{Editor: Prof.\ Peter Smith -- Comments to the Author}

### 2020-07-05 pkg/partykit/inst/ULGcourse-2020/slides_forest.Rnw
small corrections in notation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3041 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 018bf82c7d3ba542ca6499e024ddb65f1576c5d3

{\bf Idea:} \\
\begin{itemize}
\item Combine an ensemble of trees. 
\item Each tree can capture non-linear and non-additive effects and select covariates and possible interactions automatically.
\item Combining trees to a forest model allows for an approximation of smooth effects.
\item A forest can regularize and stabilize the model.
\end{itemize}

@@

$\hat{y}_t= \frac{1}{|\mathcal{B}^t_x|} \sum_{i: y_i \in \mathcal{B}^t_x} y_i$
\visible<15->{
$\ =\ \sum_{i=1}^n \frac{I(x_i \in \mathcal{B}^t_x)}{|\mathcal{B}^t_x|} \cdot y_i$
}
\visible<16->{
$\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$
}
}
\end{frame}

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Simple tree model:} Obtain the predicted response $\hat{y}$ for an observed covariate~$x$ by averaging over observations in the same terminal node $\mathcal{B}_x$: 
$$
\hat{y}= \frac{1}{|\mathcal{B}_x|} \sum_{i: y_i \in \mathcal{B}_x} y_i
\visible<2->{
\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$$
}
\visible<3->{
$$\ =\ \argmin_{\mu} \sum_{i=1}^n w_i(x) \cdot (y_i - \mu)^2$$
}

\visible<4->{
{\bf Model-based tree:} Obtain the predicted model parameter(s) $\hat{\theta}$ for an observed covariate~$x$ by optimizing a loss function for all observations in the same terminal node $\mathcal{B}_x$:
$$
\hat{\theta}= \argmin_{\theta} \sum_{i: y_i \in \mathcal{B}_x} loss(\theta; y_i)
\ =\ \argmin_{\theta} \sum_{i=1}^n w_i(x) \cdot loss(\theta; y_i)$$
}

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Strategy:} Combine trees to a forest model by employing tree-based weights.

The predicted model parameter (vector) $\hat{\theta}$ 
is the argument of the parameter space $\Theta$ 
that minimizes the weighted sum of a loss function evaluated for learning data $\{(y_i,x_i)\}_{i=1,\ldots,n}$:

@@

\begin{eqnarray*}
w^{\text{base}}_i(x)   & = & 1 \\[0.2cm]
\visible<3-4>{
w^{\text{tree}}_i(x)   & = & \sum_{b=1}^B I((x_i \in \mathcal{B}_b) \land (x \in \mathcal{B}_b)) \\[0.1cm]
\visible<4>{
w^{\text{forest}}_i(x) & = & \frac{1}{T} \sum_{t=1}^T \sum_{b=1}^{B^t} \frac{I((x_i \in \mathcal{B}^t_b) \land (x \in \mathcal{B}^t_b))}{\left|\mathcal{B}^t_b\right|}
\end{eqnarray*}
}}}

>>>>

{\bf Idea:} \\
\begin{itemize}
\item Combine an ensemble of trees. 
\item A single tree can capture non-linear and non-additive effects and select covariates and possible interactions automatically.
\item Combining trees to a forest model allows for an approximation of smooth effects.
\item A forest can regularize and stabilize the model.
\end{itemize}

@@

$\hat{y}_t= \frac{1}{|\mathcal{B}^t_x|} \sum_{i: x_i \in \mathcal{B}^t_x} y_i$
\visible<15->{
$\ =\ \sum_{i=1}^n \frac{I(x_i \in \mathcal{B}^t_x)}{|\mathcal{B}^t_x|} \cdot y_i$
}
\visible<16->{
$\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$
}
}
\end{frame}

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Simple tree model:} Obtain the predicted response $\hat{y}$ for an observed covariate~$x$ by averaging over observations in the terminal node~$\mathcal{B}_x$: 
$$
\hat{y}= \frac{1}{|\mathcal{B}_x|} \sum_{i: x_i \in \mathcal{B}_x} y_i
\visible<2->{
\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$$
}
\visible<3->{
$$\ =\ \argmin_{\mu} \sum_{i=1}^n w_i(x) \cdot (y_i - \mu)^2$$
}

\visible<4->{
{\bf Model-based tree:} Obtain the predicted model parameter(s) $\hat{\theta}$ for an observed covariate~$x$ by optimizing a loss function for all observations in the terminal node~$\mathcal{B}_x$:
$$
\hat{\theta}= \argmin_{\theta} \sum_{i: x_i \in \mathcal{B}_x} loss(\theta; y_i)
\ =\ \argmin_{\theta} \sum_{i=1}^n w_i(x) \cdot loss(\theta; y_i)$$
}

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Strategy:} Combine T trees to a forest model by employing tree-based weights.

The predicted model parameter (vector) $\hat{\theta}$ 
is the argument %of the parameter space $\Theta$ 
that minimizes the weighted sum of a loss function evaluated for learning data $\{(y_i,x_i)\}_{i=1,\ldots,n}$:

@@

\begin{eqnarray*}
w^{\text{base}}_i(x)   & = & 1 \\[0.2cm]
\visible<3-4>{
w^{\text{tree}}_i(x)   & = & \frac{I(x_i \in \mathcal{B}_x)}{\left|\mathcal{B}_x\right|}  \\[0.1cm]
\visible<4>{
w^{\text{forest}}_i(x) & = & \frac{1}{T} \sum_{t=1}^T \frac{I(x_i \in \mathcal{B}^t_x)}{\left|\mathcal{B}^t_x\right|}
\end{eqnarray*}
}}}
